The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
couple keys, couple capitals
rm todos, fix spaces, reflow, etc

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
Adult female caribou were immobilized and fitted with global positioning system
(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following
[@BJ_RNERAAS_2010] <!--TODO: fix this ref-->. We did not collar all caribou in
the herd; however, the proportion of marked adult females was ~10% of all adult
females and ~5% of all individuals in the herd. We assumed these individuals
were randomly distributed throughout the population.

## Landscape data and habitat classification
<!-- TODO: update citation for lc product from Hance --> 
Landcover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]. Available landcover classification included nine habitat
types at 30 m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broadleaf forest, and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.

@@

### Network types and construction
We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and landcover). Two season
elementary-layers (summer and winter) and three landcover elementary-layers
(forage, forest, and open) combined for a total of six layers. Single layers were
composed of individuals lnked by social associations, for each season and landcover combination. Proximity-based social
network layers were generated using the R package `spatsoc` [@Robitaille_2019]
in `r version$version.string` [@R_Core_Team_2019].
<!-- TODO: FIX VANDER WAL IN SPATSOC REF -->

@@

We weighted edges of social networks by the strength of association between
caribou using the simple ratio index (SRI, Cairns and Schwaeger 1987): 
<!-- TODO: get Cairns ref-->

@@

### Network metrics

<!-- TODO: expand + simplify + examples individual A, B etc --> 
<!-- TODO: EVW "parallelism"? -->

@@

# Scale in multilayer networks in practice: case study results and discussion
<!-- TODO: Add intro/general to results?-->

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, mean graph strength for summer networks did not
change as the social threshold increased, but graph strength in winter networks
increased rapidly between 5 m and 50 m thresholds, followed by a plateau (Figure
\@ref(fig:socres)a). Layer relevance was stable around 0 during the summer but
increased for winter networks between 5 and 50 m social thresholds, then did not
change for any habitat types (Figure \@ref(fig:socres)b). This pattern suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks. Layer similarity was
not very strong for any habitat type, indicating that summer and winter networks
are only weakly correlated. Furthermore, layer similarity in open habitats
showed more variation as social threshold increased compared to forage and
forest habitats (Figure \@ref(fig:socres)c). Connective redundancy was
relatively stable across social thresholds, especially after 50 m (Figure
\@ref(fig:socres)d). Taken together, these results suggest the optimal social
scale at which groups should be assigned is likely somewhere between ~20 - 100 m
based on the rate at which network metrics stabilized. For ungulates, groups are
often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
is likely an appropriate social scale for generating social networks in caribou
and similar species.

@@

<!-- 
TODO: Gerard ‘openness’ paper

McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics

MRSF Laforge paper 
van Beest et al. 2014 scale paper 
Habitat–performance relationships: finding the right metric at a given spatial scale
Multi-scale habitat selection modeling: a review and outlook
-->

@@

<!-- Relationship between sociality and habitat -->
<!-- Merkle’s memory and patches for bison (and leaders) -->
<!-- Emergent Properties of Conspecific Attraction inFragmented Landscapes-->
<!-- Conspecific Attraction and Aggregation in Territorial Species-->
<!-- Energy and the Scaling of Animal Space Use-->

<!-- The relationship between sociality has been discussed both theoretically -->
<!-- and tested explicitly ... CAH, etc then Fortin, McLouglin-->
<!-- https://www.pnas.org/content/pnas/105/49/19114.full.pdf
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2600907/pdf/rspb20071688.pdf
-->

@@

<!-- In summary, blah blah -->

>>>>

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
Adult female caribou were immobilized and fitted with global positioning system
(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in
the herd; however, the proportion of marked adult females was ~10% of all adult
females and ~5% of all individuals in the herd. We assumed these individuals
were randomly distributed throughout the population.

## Landscape data and habitat classification
Landcover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]. Available landcover classification included nine habitat
types at 30 m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broadleaf forest, and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.

@@

### Network types and construction
We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and landcover). Two season
elementary-layers (summer and winter) and three landcover elementary-layers
(forage, forest, and open) combined for a total of six layers. Single layers were
composed of individuals lnked by social associations, for each season and landcover combination. Proximity-based social
network layers were generated using the R package `spatsoc` [@Robitaille_2019]
in `r version$version.string` [@R_Core_Team_2019].

@@

We weighted edges of social networks by the strength of association between
caribou using the simple ratio index [SRI, @Cairns_1987]:

@@

### Network metrics 
<!-- TODO: expand + simplify + examples individual A, B etc -->

@@

# Scale in multilayer networks in practice: case study results and discussion
<!-- TODO: Add intro/general to results?-->
In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, mean graph strength for summer networks did not
change as the social threshold increased, but graph strength in winter networks
increased rapidly between 5 m and 50 m thresholds, followed by a plateau (Figure
\@ref(fig:socres)a). Layer relevance was stable around 0 during the summer but
increased for winter networks between 5 and 50 m social thresholds, then did not
change for any habitat types (Figure \@ref(fig:socres)b). This pattern suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks. Layer similarity was
not very strong for any habitat type, indicating that summer and winter networks
are only weakly correlated. Furthermore, layer similarity in open habitats
showed more variation as social threshold increased compared to forage and
forest habitats (Figure \@ref(fig:socres)c). Connective redundancy was
relatively stable across social thresholds, especially after 50 m (Figure
\@ref(fig:socres)d). Taken together, these results suggest the optimal social
scale at which groups should be assigned is likely somewhere between ~20 - 100 m
based on the rate at which network metrics stabilized. For ungulates, groups are
often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
is likely an appropriate social scale for generating social networks in caribou
and similar species.

@@

@@

@@

<!-- TODO: In summary, -->
